Rutgers Autonomous Aircraft Team\\Technical Report\\2010 AUVSI UAS Competition

### 2010-05-23 paper/paper.tex
made team list all 12 final members

The team is made of 10 Rutgers undergraduates:
\begin{tabular}{l l}
Anthony Garrison, President & Cogan Noll \\
Amanda Gaetano, Vice President & John Palmer\\
Pat Hickey, Electronics Team Leader & Adrien Perkins\\
Greg Quinn, Mechanical Team leader & Michael Varga\\
Stephen Indyk & Taras Wallace\\
\end{tabular}

\vspace{24 pt}

>>>>

The team is made of 12 Rutgers undergraduates:\\
\\ \begin{tabular}{l l}
Anthony Garrison, President & John Palmer \\
Amanda Gaetano, Vice President & Adrien Perkins\\
Pat Hickey, Electronics Team Leader & Michael Varga\\
Greg Quinn, Mechanical Team leader & Bradley Lord\\
Stephen Indyk & Taras Wallace\\ 
Cogan Noll & David Wescott\\ \\
\end{tabular}
